Analysing Constraint Grammars with a SAT-solver

### 2016-03-02 paper/lrec/eval_futurework.tex
more cleanup

A natural follow-up evaluation would be to compare the performance of the
grammar in the original state, and after removing the conflicts found
by our tool. Unfortunately, we were not able to perform such
evaluation, due to the lack of available gold standard corpora for all
the languages.

@@

The experiments revealed problems in all grammars. For the smaller
grammars, we were able to verify manually that the detected rules were
true positives.
%The results for the Finnish grammar are inconclusive, 
% For the Finnish grammar, we did not have time to
% investigate all of them, but among those we could, we found both true and false negatives.
We did not check for false negatives in any of the grammars. However, the test reported a high number of errors even in the smallest grammars, and some of them are intuitively not that bad; we

@@

%%% Nevermind, this wasn't a conflict, my program was just buggy :-P
%This is not a conflict, just pointing out an example how the SAT-solver constructs the only possible sentence where this works.

@@

This is actually a shortcoming of our way of handling the lemmas. If the lemmas and word forms were integrated to the analyses in a more feasible way, then the ambiguity class constraints would create a sequence where ``podar'' was ambiguous with ``poder'', instead of randomly chosen readings. So, even though this was not marked as a conflict, we can say that the weird output of the tool was unnecessary, and by better implementation, the tool would have created more realistic example sequence.

@@

the grammar was originally written in 1995, and converted to the
Omorfi tagset by \cite{pirinen2015}, but there were 15 rules that used the old convention for possessive suffixes.

To improve performance, we ignored the fully specified readings from the
lexicon and used only tag combinations from the grammar:
for example, the rule \texttt{REMOVE (verb sg) IF (-1 det)}
gives us ``verb sg'' and ``det''.
The shortcut works most of the time, but it is possible to
miss some cases: e.g. \texttt{SELECT PRON + REL IF (0 NOM)} 
assumes ``pron rel nom'', but our method only gives
``pron rel'' and ``nom'' separately. 
17 false positives were caused by this shortcut. 
In addition, 2 false positives were caused by the naive implementation of
rules with \verb!*! in their context.

>>>>

A natural follow-up evaluation would be to compare the performance of the
grammar in the original state, and after removing the conflicts found
by our tool. Unfortunately, we did not have time to perform such
evaluation, and in addition, we only have gold standard corpus (20~000) words for Spanish.

@@

The experiments revealed problems in all grammars. For the smaller
grammars, we were able to verify manually that the detected rules were
true positives.
%The results for the Finnish grammar are inconclusive, 
% For the Finnish grammar, we did not have time to
% investigate all of them, but among those we could, we found both true and false negatives.
We did not systematically check for false negatives in any of the
grammars, but we kept track of a number of known tricky cases; mostly
rules that had been false positives in earlier stages of the
development, and other rules with similar patterns, as well as rules
with negations.
%While this does not guarantee the lack of false negatives, it indicates some degree of reliability. 
As the tool matures and we add
new features, a more in-depth analysis will be needed.

@@

%%% Nevermind, this wasn't a conflict, my program was just buggy :-P

@@

This example shows a shortcoming of our way of handling the lemmas. If
the lemmas and word forms were integrated to the analyses in a more
feasible way, then the ambiguity class constraints would create a
sequence where ``podar'' was ambiguous with ``poder'', instead of randomly chosen readings. So, even though this was not marked as a conflict, we can say that the weird output of the tool was unnecessary, and by better implementation, the tool would have created more realistic example sequence.

@@

To improve performance, we ignored the fully specified readings from the
lexicon and used only tag combinations from the grammar:
for example, the rule \texttt{REMOVE (verb sg) IF (-1 det)}
gives us ``verb sg'' and ``det''.
The shortcut works most of the time, but it is possible to
miss some cases: e.g. \texttt{SELECT Pron + Rel IF (0 Nom)} 
may assume ``pron rel nom'' in one reading, but our method only gives
``pron rel'' and ``nom'' separately. 
17 false positives were caused by this shortcut. 
In addition, 2 false positives were caused by the naive implementation of
rules with \verb!*! in their context.
